title: "ShinyApp"
author: "Rekha Vaidyanathan"
output: html_document
runtime: shiny
---

This Shiny App demonstrates graphs plotted for the Orange dataset in R.
It executes the following steps<br><b>
(1) User's choice of Plot <br>
(2) Plots the Age and Circumference of 5 Tree types<br>
(3) Shows or Hides <i>Statistics Summary</i> calculated for Orange Dataset<br></b>

A dropdown box enables the user to select the graph type. Three types are provided.
The selectInput enables the dropdown choices and renderPlot plots the pont,line or bar graphs with the help of qplot.<br>

1. Plot <br>
2. Line Graph <br>
3. Bar Graph <br>

Based on this reactive input, selected by the user, corresponding plot/line/bar graphs are produced for the Orange Dataset. Circumference ~ Age is plotted for 5 types of trees.


```{r}
library(shiny)
library(ggplot2)
data("Orange")
inputPanel(
selectInput("UserInput",label="Choose your Graph Style", choices=c('Plot'='point', 'Line'='line','Bar'='bar'),selected='plot')
)
renderPlot ( {qplot(age, circumference, data=Orange,color=Tree,geom=input$UserInput ,stat='identity', environment=environment(),main="Graph for Orange Dataset") })

```

A checkbox in the sidepanel calculates the statistics summary.<br>
The output of which is in a
conditional panel which will show or hide this summary upon user's selection.

```{r}
inputPanel(
  checkboxInput(inputId="summary", label="Calculate Summary of data", value=FALSE)
  )
conditionalPanel("input.summary == true",renderTable(summary(Orange)))
```

